Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-26 WRITEUP/ms.tex
crushed numbers for SFE, but I think something looks wrong

A fit including the MIR 24\,$\micron$ photometry
is likely an upper limit on the \fir luminosity arising from starburst.
% since the fit include contribution from the AGN (through power-law to MIR)
If we instead fit for a model excluding the 24\,$\micron$ constraint,
two major consequences are immediately apparent.
First, the power-law index is poorly-constrained (see \Tab{SED}).
Second, the steep power-law implies a small contribution
from the power-law regime
to the total IR luminosity as compared to the graybody.
Thus, the \fir luminosity in
this model should, in principle, corresponds to a
lower limit on the cold dust emission.
Using the best-fit parameters
for this model, we find a total IR luminosity
\LIR (rest-frame 1\,$-$\,1000\,\micron) of 10.28\petm{1.89}{1.97}\E{12}\,\Lsun,
\LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
Again, the inferred quantities are uncorrected for lensing.
%The best-fit SEDs are shown in \Fig{SED} and the
% resulting parameters are listed in \Tab{SED}.

The dust temperature from both models is similar to that of
ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K; \citealt[hereafter C13]{Combes13a}).
We note the \fir luminosities from both models are comparable, which is
not surprising given the lack of constraints in the MIR. In fact, the
\fir luminosity from the second model is slightly higher than the former, but
consistent within the uncertainties.
For the subsequent analysis, we adopt the physical quantities
from the former model. The choice of which fit does not affect
the derived star formation rate (SFR) given the similar \fir luminosity.
Yet, the dust mass is higher in the former (but consistent within the
uncertainties), and thus the gas-to-dust ratio in \Sec{properties}
should be considered as an estimate.

\begin{figure*}[!htbp]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
\caption{SED models of the IR dust emission toward RXJ1131.
The data are not corrected for lensing magnification and dust extinction.
WISE flux is slightly higher than the IRAC point, probably due to a smaller
aperture used in IRAC extraction,
both of which were taken from the archive.
IRAC: Aperture flux in 5\farcs diameter.
MIPS: use PSF fit flux from archive as source size $<$ PSF FWHM of 6$^{\prime\prime}$.
Might want to add NVSS constraints.
\label{fig:SED}}
\end{figure*}

We correct for lensing using the median magnification
factor $(\mu_{\rm L}\eq5.5)$
from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
Assuming a Salpeter initial
mass function \citep{Salpeter55a}, we find a
SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
standard conversion \citep{Kennicutt98a}.
To place RXJ1131 in context of existing studies,
we compare its properties
with those reported by C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements.
Since C13 adopt a different definition of
\LFIR (40$-$500\micron)\footnote{We also note that the
\fir luminosity in C13 is derived
based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
we derive the \fir luminosity following this convention.
This yields \LFIR of $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.
This implies that RXJ1131 is considered a LIRG in regard to their
sample, and consequently, the SFR of RXJ1131 is lower
(cf. SFR\,$>$\,200, with an average of 1200). If we instead adopt the
more generally adopted total IR luminosity
classification (\LIR\,$>$\,10$^{12}$), RXJ1131 would be
considered as a ULIRG given its lensing-corrected
\LIR of $\sim$2\E{12}\,\Lsun.

@@

\subsubsection{Linewidth \& Sizes} %DONE
We find that the linewidths for both components (redshifted and blueshifted)
inferred from a double Gaussian fit to the line profile are
comparable to the C13 ULIRG sample
(FWHM of 370\,\kms). Such linewidths are higher
than local ULIRGs (240\,\kms; \citealt[][]{Solomon97a}).
Since C13 do not have resolved observations, we compare the
gas distribution with local ULIRGs. The CO gas in RXJ1131 is
distributed $\sim$6\,kpc in radius across (in
the source plane), which is more extended than the average in the
sample of disk-like ULIRGs studied by \citet{Ueda14a},
who find an average radius of 3.5\,$\pm$\,2.3\,kpc
with a range spanning 1.1$-$9.3\,kpc.
This is expected if the positive correlation in the linewidth-size relation
holds at intermediate redshifts. Yet we cannot quantify this further
with the data represented in this paper.

\subsubsection{Gas Mass}
To derive the molecular gas mass, we first correct for lensing magnification
using the respective magnification factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing. This yields
$I_{\tiny \bco}$\,=\,5.9$\pm$2.7 Jy\,\kms, where the uncertainty includes those on
the magnification factors.
We note that the derived intensity includes emission from the companion
as the spatial resolution of our data do not allow us decompose its contribution
from the total line flux.

Without direct \rot{1}{0} measurements,
we derive \rot{1}{0} intensity
using a brightness temperature ratio of $r_{\rm 32}$\,=\,1, which was chosen
solely to facilitate a comparison with the C13 sample. For the same reason, we
adopt a luminosity-to-mass conversion factor of
\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields
\Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\Lsun and a gas mass
of (2.8$\pm$1.3)\,\E{10} \Msun. This is likely
an overestimation due to a contribution from the companion, but
comparable to the C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) within the
uncertainties.

% gas-to-dyn ratio
Using the dynamical mass of BLAH (see \Sec{dynamics}), we find
a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
% gas to dust ratio:
Based on the dust mass derived from SED fitting, we find a gas-to-dust ratio of
$f_{\rm gas-dust}$\,=\,70\petm{blah}{blah}, which is consistent lower than C13
(who finds 206) sample as well as those of local (U)LIRGs
(200$-$350; Sanders et al. 1991; Contini \& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).

\subsubsection{SFE and Depletion Time}
dot dot dot

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion}
\subsection{Merger stage of RXJ1131-1231}
In this section, we put our results in context with other ULIRGs/mergers at
$z$\,=\,0$-$1. It is clear that RXJ1131 has a gas-rich companion, but how does
this affect its internal dynamics and what is the merger stage of RXJ1131?
We argued that the symmetric source-plane velocity field suggest
the system is a minor merger, consistent with an earlier study by B08, who
independently conclude that the companion is likely
a dwarf of size $\sim$700\,kpc across.

>>>>

A fit including the MIR 24\,$\micron$ photometry
is likely an upper limit on the \fir luminosity arising from starburst.
% since the fit include contribution from the AGN (through power-law to MIR)
If we instead fit for a model excluding the 24\,$\micron$ constraint,
two major consequences are immediately apparent.
First, the power-law index is poorly-constrained (see \Tab{SED}).
Second, the steep power-law implies a small contribution
from the power-law regime
to the total IR luminosity as compared to the graybody.
Thus, the \fir luminosity in
this model should, in principle, corresponds to a
lower limit on the cold dust emission.
Using the best-fit parameters
for this model, we find a total IR luminosity
\LIR (rest-frame 8\,$-$\,1000\,\micron) of 8.14\petm{2.64}{2.80}\E{12}\,\Lsun,
a \fir luminosity \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a
dust mass ($M_{\rm dust}$) of 11\petm{5}{6}\E{8}\,\Msun.
Taken at face value, this implies a \LFIR-to-\LIR
contribution of $\sim$58\%.
Again, the inferred quantities are uncorrected for lensing.
%The best-fit SEDs are shown in \Fig{SED} and the
% resulting parameters are listed in \Tab{SED}.

The dust temperature from both models is similar to that of
ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K; \citealt[hereafter C13]{Combes13a}).
We note the \fir luminosity is comparable in both models, which is
not surprising given the lack of constraints in the MIR. In fact, the
\fir luminosity from the second model is slightly higher than the former, but
consistent within the uncertainties.
For the subsequent analysis, we adopt the physical quantities
from the former (\ie with constraints at 24\,\micron).
The choice of SED model does not affect
the derived star formation rate (SFR) given the similar \fir luminosity.
Yet, the dust mass is higher in the former (but consistent within the
uncertainties), and thus the gas-to-dust ratio in \Sec{properties}
should be considered as an estimate.
We correct for lensing using the median magnification
factor $(\mu_{\rm L}\eq5.5)$
from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
Assuming a Salpeter initial
mass function \citep{Salpeter55a}, we find a
SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
standard conversion \citep{Kennicutt98a}.

\begin{figure}[!htbp]
\centering
\includegraphics[trim=65 15 15 95, clip, width=0.45\textwidth]{../Figures/FullSED.eps}
\caption{SED models of the IR dust emission toward RXJ1131.
The data are not corrected for lensing magnification and dust extinction.
{\bf This figure needs an update}
WISE flux is slightly higher than the IRAC point, probably due to a smaller
aperture used in IRAC extraction,
both of which were taken from the archive.
IRAC: Aperture flux in 5\farcs diameter.
MIPS: use PSF fit flux from archive as source size $<$ PSF FWHM of 6$^{\prime\prime}$.
Might want to add NVSS constraints.
\label{fig:SED}}
\end{figure}

To place RXJ1131 in context of existing studies,
we compare its properties
with those reported by C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements.
Since C13 adopt a different definition of
\LFIR (40$-$500\micron)\footnote{We also note that the
\fir luminosity in C13 is derived
based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
we derive the \fir luminosity following this convention.
This yields $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.
This implies that RXJ1131 is considered a LIRG in regard to their
sample, and consequently, the SFR of RXJ1131 is lower
(cf. SFR\,$>$\,200, with an average of 1200 in C13).
If we instead adopt the
more generally used definition for the total IR luminosity
(\LIR\,$>$\,10$^{12}$), RXJ1131 would be
considered a ULIRG given its lensing-corrected
total IR luminosity of $\sim$2\E{12}\,\Lsun.

@@

\subsubsection{Linewidth \& Sizes} %DONE
We find that the linewidths for both components (redshifted and blueshifted)
inferred from a double Gaussian fit to the line profile are
comparable to the C13 ULIRG sample
($\Delta v_{\rm FWHM}$ of 370\,\kms) and local ULIRGs
(300\pmm85\,\kms; \citealt[][]{Solomon97a}).
Since C13 do not have resolved observations, we compare the
gas distribution with local U/LIRGs. The CO gas in RXJ1131 is
distributed $\sim$6\,kpc in radius across (in
the source plane), which is more extended than the
sample of disk-like U/LIRGs studied by
\citet[hereafter U14]{Ueda14a}, % also classified U/LIRG using FIR from 60, 100 micron measurements
who find an average radius of 3.5\,$\pm$\,2.3\,kpc
with a range spanning 1.1\,$-$\,9.3\,kpc.
% This is expected if the positive correlation in the linewidth-size relation
% holds at intermediate redshifts. Yet we cannot quantify this further
% with the data represented in this paper.

\subsubsection{Gas Mass}
To derive the molecular gas mass, we first correct for lensing magnification
using the respective magnification factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing. This yields
$I_{\small \bco}$\,=\,5.9$\pm$2.7 Jy\,\kms,
where the uncertainty includes those on
the magnification factors.
We note that this includes emission from the companion
as the spatial resolution of our data do not allow us decompose its
contribution from the total line flux.

Without direct \rot{1}{0} measurements,
we derive \rot{1}{0} intensity
using a brightness temperature ratio of $r_{\rm 32}$\,=\,1, which was chosen
solely to facilitate a comparison with other U/LIRGs.
For the same reason, we
adopt a luminosity-to-mass conversion factor of
\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne, this yields a
CO luminosity \Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\LpU and a gas mass
$M_{\rm gas}$ of (2.8$\pm$1.3)\,\E{10} \Msun. This is likely
an overestimation for RXJ1131 due to a contribution from the companion.
The inferred gas mass is comparable to
C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) as well as
local U/LIRGs \citep{Solomon97a, Sanders96a} but higher than
local LIRGs (U14).

% gas-to-dyn ratio
We place a lower limit on the dynamical mass (see \Sec{dynamics}) using
the inferred gas mass. This BLAH.
 {\bf will need edit depending on the dyn. modeling section}
a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
% gas to dust ratio:
Using the dust mass derived from SED fitting,
we find a gas-to-dust ratio of 184\pmm124, which is consistent with
the C13 sample ($f_{\rm gas-dust}$\,=\,206) and local U/LIRGs
(200$-$350; \citealt{Sanders91a}, Contini \& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).

\subsubsection{SFE and Depletion Time}
We derive the SFE using the far-IR luminosity definition used by
C13 (\ie SFE\pmm\LFIR$($40\,$-$\,500\,\micron)$/$$M_{\rm gas}$$)$,
we find a SFE of 31\pmm15 for RXJ1131, or equivalently a depletion
timescale of $\tau$\,=\,0.19\pmm0.07\,Gyr. % 5.8/SFE
This is substantially lower than most U/LIRGs (\citealt{Combes11a}; C13,
and references therein).
\textbf{ am I doing something wrong...}

Implication of this unexpectedly low SFE in RXJ1131...

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion}
\subsection{Merger stage of RXJ1131-1231}
In this section, we put our results in context with other ULIRGs/mergers at
$z$\,=\,0\,$-$\,1. It is clear that RXJ1131 has a gas-rich companion, but how does
this affect its internal dynamics and what is the merger stage of RXJ1131?
We argued that the symmetric source-plane velocity field suggest
the system is a minor merger, consistent with an earlier study by B08, who
independently conclude that the companion is likely
a dwarf of size $\sim$700\,kpc across.
